paper1_figures

### 2023-10-05 paper1_figures.Rmd
final numbers 04.10

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

@@

node [shape = rectangle]        
rec1 [label = 'Papers identified from search engines
n = 5210']
rec2 [label = 'Duplicates
n = 624']
rec3 [label = 'Papers screened based on titles and abstracts
n = 4586']
rec4 [label = 'Papers not suitable
n = 4321']
rec5 [label = 'Papers read completely
n = 265']
rec6 [label = 'Papers not suitable
n = YYY']
rec7 [label = 'Studies included
n = XXX']

>>>>

@@

node [shape = rectangle]        
rec1 [label = 'Papers identified from search engines
n = 5210']
rec2 [label = 'Duplicates
n = 624']
rec3 [label = 'Papers screened based on titles and abstracts
n = 4586']
rec4 [label = 'Papers not suitable
n = 4333']
rec5 [label = 'Papers read completely
n = 253']
rec6 [label = 'Papers not suitable
n = 157']
rec7 [label = 'Studies included
n = 96']
